Supplementary Content

### 2022-03-14 experiments/2_supplement/supplement.Rmd
supplement.Rmd: fixed paths
parameter_master is missing.

```{r echo = FALSE}
rm(list = ls())
library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("r/various_useful_functions.r"))
source(here("experiments/1_figures_main_ms/ms_figure_functions.r"))

@@

```{r repl_meth1, echo=FALSE, eval = TRUE}
repl_meth <- readRDS(here("data/0_ss_finding/replication_method/ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
temp_meth <- readRDS(here("data/0_ss_finding/temporal_method/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
```

@@

```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))

@@

```{r div-temp-eventdef1, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data/0_ss_finding/temporal_method/event_def1/processed_data/stab_data_temporal_method.RDS"))

@@

```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))

@@

```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
single_1e6 <- readRDS(here("data/0_ss_finding/temporal_method/single_1e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_1e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
single_2e6 <- readRDS(here("data/0_ss_finding/temporal_method/single_2e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_2e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here(paste0("data/0_ss_finding/temporal_method/ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here(paste0("data/0_ss_finding/temporal_method/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

```{r eval = run_sims_this_section, echo = FALSE}
#var_expt <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
var_expt_levels <- var_expt[,1:6]
no_diversity <- which(rowSums(abs(var_expt_levels))==0)
max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
                            rowSums(abs(var_expt_levels)))
max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
                            rowSums(abs(var_expt_levels[,1:2])) &
                              rowSums(abs(var_expt_levels[,3:6]))==0)
max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)
```

@@

sim_res_novar1 <- run_simulation(parameter)
saveRDS(sim_res_novar1, here("experiments/checks_puzzles/data/puzzle1_1.RDS"))
```

@@

```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_novar1 <- readRDS(here("experiments/2_supplement/data/puzzle1_1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

```{r  eval = run_sims_this_section, echo = FALSE}
parameter$strain_parameter <- var_expt[max_only_SBPB_diversity,]$pars[[1]]
#parameter$sim_duration <- 100000
#parameter$result <- NULL
#parameter$log10a_series <- c(-5.2, -5.2)
#parameter$strain_parameter$initial_state <- new_initial_state(
#  nrow(parameter$strain_parameter$CB),
#  nrow(parameter$strain_parameter$PB),
#  nrow(parameter$strain_parameter$PB),
#  values = "bush_ssfig3"
#)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/checks_puzzles/data/puzzle1_2.RDS"))
```

@@

```{r sb-div-effect4, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect4)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_highvar1 <- readRDS(here("experiments/2_supplement/data/puzzle1_2.RDS"))
plot_dynamics(sim_res_highvar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r echo = FALSE}
ss_9s <- readRDS(here("data/0_ss_finding/temporal_method/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
only_PB_variable <- ss_9s %>%
  filter(
    abs(CB_var_gmax_s) < 0.0001,
    abs(SB_var_gmax_s) < 0.0001
  )
only_PB_variable <- only_PB_variable[order(only_PB_variable$PB_var_gmax_s), ]

only_PB_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS")) %>%
  filter(
    num_strains == 9,
    waittime == 1e6,
    var_treat == "PB",
    Species == "SB_tot"
  )
only_PB_stab <- only_PB_stab[order(only_PB_stab$PB_var_gmax_s), ]

@@

stab_9s <- readRDS(here("data/0_ss_finding/temporal_method/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))

@@

```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS")) 
which_strains <- c(2, 3, 6, 9)
which_wait_time<- 1e6
figure_title <- " "

>>>>

```{r echo = FALSE}
rm(list = ls())
library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("r", "various_useful_functions.r"))
# source(here("experiments", "1_figures_main_ms", "ms_figure_functions.r"))
source(here("experiments", "1_figures_main_ms", "figures_main_ms_v1.R"))

@@

```{r repl_meth1, echo=FALSE, eval = TRUE}
repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
temp_meth <- readRDS(here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
```

@@

```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data", "0_ss_finding", "replication_method", "processed_data", "stab_data_replication_method.RDS"))

@@

```{r div-temp-eventdef1, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "event_def1", "processed_data", "stab_data_temporal_method.RDS"))

@@

```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS"))

@@

```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
single_1e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_1e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_1e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
single_2e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_2e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_2e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

```{r eval = run_sims_this_section, echo = FALSE}
#var_expt <- readRDS(here::here("data", "9_strains", "ss_data_1e6_x2x6_factorial.RDS"))
var_expt_levels <- var_expt[,1:6]
no_diversity <- which(rowSums(abs(var_expt_levels))==0)
max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
                            rowSums(abs(var_expt_levels)))
max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
                            rowSums(abs(var_expt_levels[,1:2])) &
                              rowSums(abs(var_expt_levels[,3:6]))==0)
max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)
```

@@

sim_res_novar1 <- run_simulation(parameter)
dir.create(here::here("data", "2_supplement"), recursive = TRUE, showWarnings = FALSE)
saveRDS(sim_res_novar1, here::here("data", "2_supplement", "puzzle1_1.RDS"))
```

@@

```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_novar1 <- readRDS(here::here("data", "2_supplement", "puzzle1_1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)
```

```{r  eval = run_sims_this_section, echo = FALSE}
parameter$strain_parameter <- var_expt[max_only_SBPB_diversity,]$pars[[1]]
#parameter$sim_duration <- 100000
#parameter$result <- NULL
#parameter$log10a_series <- c(-5.2, -5.2)
#parameter$strain_parameter$initial_state <- new_initial_state(
#  nrow(parameter$strain_parameter$CB),
#  nrow(parameter$strain_parameter$PB),
#  nrow(parameter$strain_parameter$PB),
#  values = "bush_ssfig3"
#)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1,here::here("data", "2_supplement", "puzzle1_2.RDS"))
```

@@

```{r sb-div-effect4, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect4)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_highvar1 <- readRDS(here("data", "2_supplement", "puzzle1_2.RDS"))
plot_dynamics(sim_res_highvar1)
#ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)
```

@@

```{r echo = FALSE}
ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
only_PB_variable <- ss_9s %>%
  filter(
    abs(CB_var_gmax_s) < 0.0001,
    abs(SB_var_gmax_s) < 0.0001
  )
only_PB_variable <- only_PB_variable[order(only_PB_variable$PB_var_gmax_s), ]

only_PB_stab <- readRDS(here::here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS")) %>%
  filter(
    num_strains == 9,
    waittime == 1e6,
    var_treat == "PB",
    Species == "SB_tot"
  )
only_PB_stab <- only_PB_stab[order(only_PB_stab$PB_var_gmax_s), ]

@@

stab_9s <- readRDS(here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))

@@

```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS")) 
which_strains <- c(2, 3, 6, 9)
which_wait_time<- 1e6
figure_title <- " "
